The Ranked Nearest Neighbour Interchange space

### 2019-06-27 paper.tex
a few general comments

This paper is an advance towards the general goal of understanding the geometry of the $\rnni$ space.

Algorithm~\ref{alg:find_path} computes paths between pairs of trees in $\rnni$ and will be a central tool for our investigation of shortest paths in $\rnni$.

@@

\todo{figure of an example? Brief explanation what algorithm does?}

One can easily prove that there is always exactly one $\rnni$ move on $T$ that decreases the rank of $mrca_T(C)$ as in line~\ref{alg:line:move_set_down} of Algorithm~\ref{alg:find_path}.
It follows that Algorithm~\ref{alg:find_path} returns a path in $\rnni$ for any pair of trees $T,R$.
Moreover, it gives an upper bound for the diameter of $\rnni$, which improves the one given in \autocite{Gavryushkin2017}:

\begin{lemma}
    It is $\Delta(\rnni) \leq \frac{(n-1)(n-2)}{2}$.
\end{lemma}

>>>>

This paper is an advance towards the general goal of understanding the geometry of the $\rnni$ space.
%TODO
In this section, we...

We now present an efficient algorithm (Algorithm~\ref{alg:find_path}) for computing paths between pairs of trees in $\rnni$.
This algorithm will be a central tool for our investigation of shortest paths in $\rnni$.

%TODO
The idea of the algorithm is the following...

@@

\todo{This text comes out of the blue.
Generally, before going into explanations like this it's a good idea to say what's ahead.}
One can easily prove that there is always exactly one $\rnni$ move on $T$ that decreases the rank of $mrca_T(C)$ as in line~\ref{alg:line:move_set_down} of Algorithm~\ref{alg:find_path}.
It follows that Algorithm~\ref{alg:find_path} returns a path in $\rnni$ for any pair of trees $T,R$.
\todo{This should have been stated before, where you say what is going on.}
Moreover, it gives an upper bound for the diameter of $\rnni$, which improves the one given in \autocite{Gavryushkin2017}:

\begin{lemma}
%TODO: here and generally, I prefer introducing definitions like this as you go but it's the matter of preference so up to you.
$\Delta(\rnni) \leq \frac{(n-1)(n-2)}{2}$, where $\Delta$ is...
\end{lemma}
